On resolution sensitivity in the Community Atmosphere Model

### 2019-09-15 resolution.tex
edits

The $n=-1$ power law scaling is potentially in conflict with the scaling proposed by \cite{RETAL2016CD}, $n=h-1$, with $h$ being half the exponent of the second-order structure function $\Delta x^{2h}$ of the horizontal wind. \cite{RETAL2016CD} propose that since the $h=\frac{1}{3}$ is supported by observations, it is an emergent constraint for $n=-\frac{2}{3}$. This is an intriguing proposal and the authors don't seek to dismiss its potential value. But it is suggested that the overwhelming support for the $h=\frac{1}{3}$ exponent in the second-order structure function is only relevant for horizontal scales on the order of $100$ km and less \citep{L1999JFM,CL2001JGR}, which is only marginally resolved in the highest resolution simulation $\Delta x=27.8$ km ($ne120$), and CAM-SE-CSLAM has an effective resolution in the range of $5-10\Delta x$ \citep{HETAL2019JAMES}. The nonexistence of $h=\frac{1}{3}$ in the $\Delta x=27.8$ km simulation is verified through analyzing the slope of kinetic energy spectrum $-\beta$, which is in duality with the second-order structure function through the Weiner–Khinchine theorem. For $h=\frac{1}{3}$, $\beta=\frac{5}{3}$, which is shallower than the slope observed near the effective resolution for all grid resolutions in this study (Figure~~\ref{fig:2ke}). There is however, a progressive shoaling of the slope $-\beta$ with increasing resolution (Figure~~\ref{fig:2ke}b). This suggests a transition towards the $-\frac{5}{3}$ slope in the model, but seeing this process through would require running the model at higher resolutions than considered in this study.

\begin{figure}
\begin{center}
\noindent\includegraphics[width=20pc,angle=0]{figs/temp_kespectra.pdf}\\
\end{center}
\caption{(a) Kinetic energy spectrum and (b) compensated kinetic energy spectrum at the 200 hPa level in the simulations. The diagonal black line in (a) is a reference spectrum with a $-3$ slope. Compensated kinetic energy spectrum refers to the kinetic energy spectrum multiplied by $n^{-\frac{5}{3}}$, with $n$ the spherical wavenumber, so that horizontal lines indicate a spectrum with a $-\frac{5}{3}$ slope. All resolutions in this study have a slope of the kinetic energy spectrum steeper than $-\frac{5}{3}$ near the effective resolution of the model.}
\label{fig:2ke}
\end{figure}

>>>>

The $n=-1$ power law scaling is potentially in conflict with the scaling proposed by \cite{RETAL2016CD}, $n=h-1$, with $h$ being half the exponent of the second-order structure function $\Delta x^{2h}$ of the horizontal wind. \cite{RETAL2016CD} propose that since the $h=\frac{1}{3}$ is supported by observations, it is an emergent constraint for $n=-\frac{2}{3}$. This is an intriguing proposal and the authors don't seek to dismiss its potential value. But it is suggested that the overwhelming support for the $h=\frac{1}{3}$ exponent in the second-order structure function is only relevant for horizontal scales on the order of $100$ km and less \citep{L1999JFM,CL2001JGR}, which is only marginally resolved in the highest resolution simulation $\Delta x=27.8$ km ($ne120$), and CAM-SE-CSLAM has an effective resolution in the range of $5-10\Delta x$ \citep{HETAL2019JAMES}. The nonexistence of $h=\frac{1}{3}$ in the $\Delta x=27.8$ km simulation is verified through analyzing the slope of the kinetic energy spectrum $-\beta$, which is in duality with the second-order structure function through the Weiner–Khinchine theorem. For $h=\frac{1}{3}$, $\beta=\frac{5}{3}$, which is shallower than the slope near where the spectrum approaches the effective resolution, for all grid resolutions (Figure~~\ref{fig:2ke}). There is however, a progressive shoaling of the slope $-\beta$ with increasing resolution (Figure~~\ref{fig:2ke}b). This suggests a transition towards the $-\frac{5}{3}$ slope in the model, but seeing this process through would require running the model at higher resolutions than considered in this study.

\begin{figure}
\begin{center}
\noindent\includegraphics[width=20pc,angle=0]{figs/temp_kespectra.pdf}\\
\end{center}
\caption{(a) Kinetic energy spectrum and (b) compensated kinetic energy spectrum at the 200 hPa level in the simulations. The diagonal black line in (a) is a reference spectrum with a $-3$ slope. Compensated kinetic energy spectrum refers to the kinetic energy spectrum multiplied by $n^{-\frac{5}{3}}$, with spherical wavenumber $n$, so that horizontal lines indicate a spectrum with a $-\frac{5}{3}$ slope. In (b), thick ``caterpillars" are overlain on the portion of each spectrum pertaining to the $5-10 \Delta x$ effective resolution of the model.}
\label{fig:2ke}
\end{figure}
